Data Specialization for a Staged Lambda Calculus

### 2015-02-27 paper/overview.tex

Our type system ensures that the staging annotations are consistent,
in the sense that computations marked as first-stage cannot depend on
ones marked as second-stage.
%
The process of adding staging annotations to unstaged code has been
the subject of extensive research (\secref{related}). We assume that
these annotations have been provided; we do not consider the problem
of generating them. In this example, there are other ways to annotate
\texttt{qs}, but we chose annotations that maximize the work performed
in the first stage

@@

When applied to the quick-select example as described, our splitting
algorithm yields a two-pass program that uses the binary-search-tree
based implementation outlined above.  Specifically, in the first pass,
the program takes the input list and constructs a probabilistically
balanced binary search tree, which is isomorphic to a treap data
structure~\cite{treaps}.  In the second pass, the program performs,
for each rank, a binary search tree lookup, by walking the tree to
find the element with the desired rank.  The resulting program, shown
in \ref{fig:????}  takes the $O(n\log{n} + m\log{n})$.

>>>>

Our type system ensures that the staging annotations are consistent,
in the sense that computations marked as first-stage cannot depend on
ones marked as second-stage.
%
The process of adding staging annotations to unstaged code has been
the subject of extensive research (\ref{sec:related}). We assume that
these annotations have been provided; we do not consider the problem
of generating them. In this example, there are other ways to annotate
\texttt{qs}, but we chose annotations that maximize the work performed
in the first stage

@@

When applied to the quick-select example as described, our splitting
algorithm yields a two-pass program that uses the binary-search-tree
based implementation outlined above.  Specifically, in the first pass,
the program takes the input list and constructs a probabilistically
balanced binary search tree, which is isomorphic to a treap data
structure~\cite{treaps}.  In the second pass, the program performs,
for each rank, a binary search tree lookup, by walking the tree to
find the element with the desired rank.  The resulting program, shown
in \ref{fig:qs-split}  takes the $O(n\log{n} + m\log{n})$.
